Assessing glymphatic transport velocities by adjoint methods

### 2018-10-12 tex/paper.tex
reelle data, lagt til

\subsection{MRI Data} 
The MRI data consisted of the observations at times $t_i \in \lbrace$ 0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24.06, 47.84, 698.02 $\rbrace (hours)$ with the time $t_i=0.00$ as the observation 1-2 hours after the tracer was injected. There was no significant visible change in the tracer between the observations at $\lbrace 0.00 0.16, 0.39, 0.55, 0.77 \rbrace$. This prompted the focus on the observation times  $0.00 2.09, 6.05, 24.06, 47.84$, which can be seen in Fig.??.

The estimation of tracer concentration proved difficult in the CSF compartment. Therefore the 2 domain mesh, shown in Fig.\ref{figmesh} was used in the computation. Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $gtol=6.0e-1$. The resulting states can be seen in Fig. ?? and the relative error of control values are displayed in Tab.?? .

\subsection*{DTI comparison}
The median diffusion coefficient in the DTI was estimated to be respectively in white and grey matter to be 8.7e-4 $\mathrm{mm\sp{2}/s}$ and  1.0e-3 $\mathrm{mm\sp{2}/s}$. %This corresponds to 3.1 $\mathrm{mm\sp{2}/h}$ and  3.6 $\mathrm{mm\sp{2}/h}$. 
The self-diffusivity of water have been estimated to be about  3.0e-3$\mathrm{mm\sp{2}/s}$ at 37\sp{o}C.% This corresponds to 10.8 $\mathrm{mm\sp{2}/h}$ and  $\mathrm{mm\sp{2}/h}$.

This is an increase from the reported values in [insert citation] of XX and XX.

@@

\subsection{Anisotropy}
The computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown in Fig\ref{FIG::DTI}.

The anisotropy can be seen by comparing the observations and the states after 48 hours, see Fig ??. This observation is after 48 hours, and the amount of tracer inside the anisotropic region is negligible. Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can asses a static environment.

A more important factor is that of tissue damage, which may causes higher diffusivity.  In Fig.\ref{FIG::DTI}, it can be observed that the region with high diffusivity also have a high concentration tracer, see Fig ??. Since resulting states corresponds with the observation indicates that the computed values are higher than the average ADC value.

\subsection{Real Data}

The computed diffusion coefficients are in the same magnitude as the values obtained from the DTI. But it can be seen that there is a clear difference between grey matter and white matter values.

The grey matter diffusion coefficient displays a high volatility in the variation of the relaxation parameters, which can be seen in Tab.\ref{Tab::Real-data}. This volatility can be caused by the boundary control $g$, which exists along the entire boundary of the grey matter. Considering the that the grey matter volume has a depth less than 5 mm makes it susceptible to changes in $g$. Therefore this seems likely, given the fact that both relaxation parameters are used to adjust the boundary control.

 boundary control, which exists along the external boundary of the grey matter. This

@@

The computational have two values for diffusion coefficients, while it can be seen in  Fig.\ref{FIG::DTI} that diffusion coefficients can be considered a spacial function. 
The controls for diffusion coefficients should be spacial functions, but this would increase the computational cost greatly.

@@

The concentration estimation is a stepwise process, which required adjustment of the intensity for each observation \cite{eidevalnes}. Thus the accumulation of errors can be a factor in the estimation.

The results of the computation using MRI data show a higher volatility of the regularization parameters.

\section{Conclusion}
The results from the manufactured

However, this method has limitations based on the model and on the acquired data.

The adaptation for a

\begin{figure}
\centering
\includegraphics[scale=0.4]{27-12-hours-scale-0-1-3.png}  
\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15. C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$. D) Shows the resulting state given the observation in A. E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C. }
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.4]{27-24-hours-scale-0-1.png}
\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15 {\color{red} explain noise ampliutde}. C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$. D) Shows the resulting state given the observation in A. E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.  }
\end{figure}

@@

 \begin{table}
\centering
\caption{ {\color{red} Preliminary data, new runs with different convergence criteria is running. No excepted change is assumed see Fig.\ref{fig:gull} } Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the estimated diffusion coefficients based on MRI data.}
\resizebox{\textwidth}{!}{\begin{tabular}{*{6}c}
$\alpha$ & $\beta$ & k & iter &  $ ||D_{\Omega_1}||_{RE}$ & $ ||D_{\Omega_2}||_{RE}$ \\
\hline
 1.0e-02 	 & 1.0e+00 	 & 24 & 1001 	 & +0.658 & +0.914 \\ 
 1.0e-02 	 & 1.0e-02 	 & 24 & 1001 	 & +0.840 & +0.976 \\ 
 1.0e-06 	 & 1.0e+00 	 & 24 & 1001 	 & +0.572 & +0.832 \\ 
 1.0e-06 	 & 1.0e-02 	 & 24 & 1001 	 & +0.719 & +0.727 \\

@@

\begin{figure}
  \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Pic_Grey.png}
        \caption{ {\color{red} shows that it converges but sufficent to the convergence criteria}}
        \label{fig:gull}
    \end{subfigure}
     \qquad
     \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Pic_White.png}
        \caption{ {\color{red} shows that it converges but sufficent to the convergence criteria} }
        \label{fig:gull}
    \end{subfigure}
\end{figure}

>>>>

\subsection{MRI Data} 
The MRI data consisted of the observations at times $t_i \in \lbrace$ 0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24.06, 47.84, 698.02 $\rbrace (hours)$ with the time $t_i=0.00$ as the observation 1-2 hours after the tracer was injected. There was no significant visible change in the tracer between the observations at $\lbrace 0.00 0.16, 0.39, 0.55, 0.77 \rbrace$. This prompted the use of the following observation times  $0.00 2.09, 6.05, 24.06, 47.84$.

The estimation of tracer concentration proved difficult in the CSF compartment. Therefore the 2 domain mesh, shown in Fig.\ref{figmesh} was used in the computation. The boundary control was set to the external boundary of both domains, and the subscript in $D_w$ and $D_g$ denotes white and grey diffusion coefficients. Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $gtol=6.0e-1$.

The results are shown in Tab.\ref{Tab::Real-data}, 
and the observation together with resulting states are displayed in Fig.\ref{Fig::realdata}

\subsection*{DTI comparison}
The median diffusion coefficient in the DTI was estimated to be 8.7e-4 $\mathrm{mm\sp{2}/s}$ in   white matter and 1.0e-3 $\mathrm{mm\sp{2}/s}$ in grey matter.   %This corresponds to 3.1 $\mathrm{mm\sp{2}/h}$ and  3.6 $\mathrm{mm\sp{2}/h}$. 
The self-diffusivity of water have been estimated to be around 3.0e-3$\mathrm{mm\sp{2}/s}$ for  $37\sp{o}C$.% This corresponds to 10.8 $\mathrm{mm\sp{2}/h}$ and  $\mathrm{mm\sp{2}/h}$.

The reference value of Gd-DPTA was reported to be 3.8e-4 $\mathrm{mm\sp{2}/s}$ in [insert citation]. The values in Tab.\ref{Tab::Real-data} gives the value-range $1.5e-4 -2.7e-4\mathrm{mm\sp{2}/s}  $ for the grey diffusion coefficient and  $2.2e-4 - 3.3e-4\mathrm{mm\sp{2}/s}$ for the white diffusion coefficient. These values are $20 -110 \%$ larger than the expected values for $D_{g}$,  and $100 - 200 \%$ larger than the expected values for $D_{w}$.

The estimation assumes that the tortousity is independent on molecular size.

%The region with high diffusivity in the white matter, shown in Fig\ref{FIG::DTI}, gives a upper bound on the diffusion coefficient to be 1.3 $\mathrm{mm\sp{2}/s}$.

%
% \begin{table}
%\centering
%\caption{Viser omgjøringer,estiamering og prosentvis forskjell for min og max control/optimerte verdier . Unit $\left[ \mathrm{mm\sp{2}/h} \right]$}
%\resizebox{\textwidth}{!}{\begin{tabular}{*{6}c}
%$ D\sp{free}_{water} $ & $ D\sp{DTI}__{g} $ & $ D\sp{DTI}_{w} $ & $D\sp{fre}__{Gd-DPTA} $ & $D\sp{ADC}__{g} $ & $ D\sp{ADC}_{w} $ & $ D\sp{ADC}_{g} -D\sp{OPT}_{g} $ &$ D\sp{ADC}_{w} -D\sp{OPT}_{w} $ \\
%\hline
%10.8 & 3.64 & 3.13 & 1.37 & 0.46 & 0.40 &  20 - 114 $\%$  & 100- 200 $\%$
%  -   &  -    & 4.86 &  - &  -   & 0.61 &   -                  &   0 - 100 $\%$       
%\end{tabular}} 
%\label{}
%\end{table} 
%

{\color{red} tortuoisty mindre for støre molekyler ? }
%The region with high diffusivity in the white matter, shown in Fig\ref{FIG::DTI}, gives a upper bound on the diffusion coefficient to be 1.3 $\mathrm{mm\sp{2}/s}$

@@

The computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{FIG::DTI}. The region with high FA, can also be observed in the observation after 48 hours, shown in Fig.\ref{Fig::realdata}. This observation is after 48 hours, and the amount of tracer inside the anisotropic region is negligible. Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment. Thus observation of tracer in anisotropic regions are needed for the integration of anisotropy into the model.

A more important factor are regions with higher diffusivity. In Fig.\ref{FIG::DTI}, it can be observed that the region with high diffusivity also have a high tracer concentration, see Fig \ref{Fig::realdata}.

The computational have 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{FIG::DTI} that diffusion coefficients can be considered a spacial function.

In Tab.\ref{Tab::Real-data}, it is shown that the grey matter diffusion coefficient have a consistent increase based on the decrease in the relaxation parameter $\beta$. This can be caused by the boundary control $g$, which exists along the entire boundary of the grey matter. Considering the that the grey matter volume has a depth less than 5 mm makes it susceptible to changes in $g$. Therefore this seems likely, given the fact that both relaxation parameters are used to adjust the boundary control.

@@

@@

\section{Conclusion}

%\begin{figure}
%\centering
%\includegraphics[scale=0.4]{27-12-hours-scale-0-1-3.png}  
%\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15. C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$. D) Shows the resulting state given the observation in A. E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C. }
%\end{figure}
%
%
%\begin{figure}
%\centering
%\includegraphics[scale=0.4]{27-24-hours-scale-0-1.png}
%\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15 {\color{red} explain noise ampliutde}. C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$. D) Shows the resulting state given the observation in A. E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.  }
%\end{figure}
% 
% 
% 
%
%

@@

 \begin{table}
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the estimated diffusion coefficients for grey $D_g$ and white $D_w$ matter based on MRI data.}
\resizebox{\textwidth}{!}{\begin{tabular}{*{6}c}
$\alpha$ & $\beta$ & k & iter &  $ D_{g} \left[ \mathrm{mm\sp{2}/h} \right] $ & $ D_{w} \left[ \mathrm{mm\sp{2}/h} \right]$ \\
\hline
 1.0e-02 	 & 1.0e+00 	 & 48 & 591 	 & 0.648 & 0.893 \\ 
 1.0e-02 	 & 1.0e-01 	 & 48 & 461 	 & 0.772 & 0.982 \\ 
 1.0e-02 	 & 1.0e-02 	 & 48 & 748 	 & 0.986 & 1.198 \\ 
 1.0e-04 	 & 1.0e+00 	 & 48 & 607 	 & 0.551 & 0.815 \\ 
 1.0e-04 	 & 1.0e-01 	 & 48 & 598 	 & 0.649 & 0.787 \\ 
 1.0e-04 	 & 1.0e-02 	 & 48 & 837 	 & 0.740 & 0.817 \\ 
 1.0e-06 	 & 1.0e+00 	 & 48 & 681 	 & 0.557 & 0.811 \\ 
 1.0e-06 	 & 1.0e-01 	 & 48 & 780 	 & 0.645 & 0.774 \\ 
 1.0e-06 	 & 1.0e-02 	 & 48 & 745 	 & 0.736 & 0.819 \\

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{different.png} 
\caption{Row A) shows the observation at times 2 hours, 6 hours, 24 hours and 48 hours after the first observation with tracer. Row B) shows the corresponding states with the relaxation parameters set to $ \alpha=0.01$ and $\beta=0.01$.   Row C) shows the corresponding states with the relaxation parameters set to $ \alpha=0.0001$ and $\beta=1.0$.
 Row D) shows the corresponding states with the relaxation parameters set to$ \alpha=1.0e-6$ and $\beta=0.1$. The color-bar was restricted to the range $ \lbrace 0 ,0.5 \rbrace$. }
\label{Fig::realdata}
\end{figure}
